The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-05-24 ms.Rmd

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = "hide", results = "hide", message = FALSE, fig.height = 9, fig.width = 9}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap)
```

@@

```{r merowworkflowtemp, eval = TRUE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Background(n = 10000),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PrintMap))
```

@@

Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Chain(Transform(trans = 'square',
                                 replace = FALSE), 
                       Background(n = 10000)),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap, Coefficients))
```

>>>>

```{r fengworkflow, eval = TRUE, dpi = 300, fig.show = "hide", results = "hide", message = FALSE, fig.height = 9, fig.width = 9}
Feng_Papes <- 
  workflow(occurrence = SpOcc('Dasypus novemcinctus',
                              extent = c(-130, -20, -60, 60)),
            covariate = Bioclim(extent = c(-130, -20, -60, 60),
                                layers = c(1:4, 6, 9, 10, 12, 15)),
              process = Chain(Clean, 
                              MESSMask,  
                              Background(n = 10000, bias = 200), 
                              Crossvalidate(k = 5)),
                model = MaxEnt,
               output = PrintMap(points = FALSE))
```

@@

```{r merowworkflowtemp, eval = TRUE}
Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Background(n = 10000),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PrintMap(points = FALSE)))
```

@@

Merow_Silander <- workflow(
    occurrence = CarolinaWrenPO,
    covariate = CarolinaWrenRasters,
    process = Chain(Transform(trans = 'square',
                                 replace = FALSE), 
                       Background(n = 10000)),
    model = list(LogisticRegression, MaxEnt, MaxLike),
    output = Chain(PerformanceMeasures, PointBiserialCorr, PrintMap(points = FALSE), Coefficients))
```
